|

### 2021-08-16 paper/dcpo_demsupport.Rmd
use dotwhisker::small_multiple for APSR plot (but legend); add title to AJPS plot; clean up

# ```{r coefName-AJPS}
# index_coefName <- c(
#     `Democracy\n (t-1)` = "Democracy[t-1]",
#     `Democracy\n (t-2)` = "Democracy[t-2]",
#     `Support\n (t-1)` = "Support[t-1]",
#     `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
#     `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
#     `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
#     `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
#     `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
#     `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
#     `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
# )
# ```

@@

df_plot <- bind_rows(result_pooledAJPS, result_regimeAJPS) %>% 
    mutate(term = case_when(term0 == 'Democracy\n (t-1)' ~ "Democracy[t-1]",
                            term0 == 'Democracy\n (t-2)' ~ "Democracy[t-2]",
                            term0 == 'Support\n (t-1)' ~ "Democratic~Support[t-1]",
                            term0 == 'Support\n demo only\n (t-1)' ~ "Democratic~Support[t-1]~(democracies)",
                            term0 == 'Support\n auto only\n (t-1)' ~ "Democratic~Support[t-1]~(autocracies)",
                            term0 == 'Log GDP\n per capita\n (t-1)' ~ "Log~GDP~per~capita[t-1]",
                            term0 == 'GDP per\n capita growth\n (t-1)' ~ "GDP~per~capita~growth[t-1]",
                            term0 == 'Regional\n democracy\n (t-1)' ~ "Regional~Democracy[t-1]",
                            term0 == 'Percent\n Muslim\n (t-1)' ~ "Percent~Muslim[t-1]",
                            term0 == 'Resource\n dependence\n (t-1)' ~ "Resource~Dependence[t-1]",
                            TRUE ~ str_replace(term0, " ", "~")), 
           term = factor(term, levels =  c(
               "Democracy[t-1]",
               "Democracy[t-2]",
               "Democratic~Support[t-1]",
               "Democratic~Support[t-1]~(democracies)",
               "Democratic~Support[t-1]~(autocracies)",
               "Log~GDP~per~capita[t-1]",
               "GDP~per~capita~growth[t-1]",
               "Regional~Democracy[t-1]",
               "Percent~Muslim[t-1]",
               "Resource~Dependence[t-1]")))

small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
    theme_bw() +
    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
    scale_color_grey(start = 0.8, end = 0.4, 
                     name = "Replication",
                     breaks=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data"),
                     labels=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")) +
    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
          strip.text.y.left = element_text(angle = 0),
          legend.position = c(-0.115, -.01),
          legend.justification = c(1, 1), 
          legend.title = element_text(size = 9, face = "bold"),
          legend.title.align = 0.5,
          legend.text = element_text(size = 9),
          legend.background = element_rect(color="gray90"),
          legend.spacing = unit(-3, "pt"),
          legend.key.size = unit(9, "mm"))

@@

@@

@@

@@

```{r coefName-APSR}
index_coefName <- c(
    `Democratic Mood\n (t-1)` = "Support[t-1]",
    `Democratic Mood\n (t-2)` = "Support[t-2]",
    `Liberal Democracy\n (Difference)` = "Delta~Liberal~democracy",
    `Liberal Democracy\n (t-1)` = "Liberal~democracy[t-1]",
    `Electoral Democracy\n (Difference)` = "Delta~Electoral~democracy",
    `Electoral Democracy\n (t-1)` = "Electoral~democracy[t-1]",
    `Minoritarian Democracy\n (Difference)` = "Delta~Minoritarian~democracy",
    `Minoritarian Democracy\n (t-1)` = "Minoritarian~democracy[t-1]",
    `Log GDP\n per capita\n (Difference)` = "Delta~Log~GDP~per~capita",
    `Log GDP\n (t-1)` = "Log~GDP[t-1]"
)
```

```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10}
type_model <-
    c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")

df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>%
    mutate(
        term = index_coefName[term],
        term = factor(term, levels = unique(index_coefName)),
        type = factor(type, levels = c("Pooled", "Institution Specified"))
    )

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    ggtitle("DV: The Change of Public Support for Democracy") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    facet_wrap(~ type)  +
    scale_color_gb(palette = "digitMixed")

>>>>

```{r coefName-AJPS}
index_coefName <- c(
    `Democracy\n (t-1)` = "Democracy[t-1]",
    `Democracy\n (t-2)` = "Democracy[t-2]",
    `Support\n (t-1)` = "Democratic~Support[t-1]",
    `Support\n demo only\n (t-1)` = "Democratic~Support[t-1]~(democracies)",
    `Support\n auto only\n (t-1)` = "Democratic~Support[t-1]~(autocracies)",
    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~Growth[t-1]",
    `Regional\n democracy\n (t-1)` = "Regional~Democracy[t-1]",
    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
    `Resource\n dependence\n (t-1)` = "Resource~Dependence[t-1]"
)
```

@@

df_plot <- bind_rows(result_pooledAJPS, result_regimeAJPS) %>% 
  mutate(term = index_coefName[term0], 
           term = factor(term, levels = unique(index_coefName)))

small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
    theme_bw() +
    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
    scale_color_grey(start = 0.8, end = 0.4, 
                     name = "Replication",
                     breaks=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data"),
                     labels=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")) +
    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
          strip.text.y.left = element_text(angle = 0),
          legend.position = c(-0.115, -.01),
          legend.justification = c(1, 1), 
          legend.title = element_text(size = 9, face = "bold"),
          legend.title.align = 0.5,
          legend.text = element_text(size = 9),
          legend.background = element_rect(color="gray90"),
          legend.spacing = unit(-3, "pt"),
          legend.key.size = unit(9, "mm")) +
  ggtitle("DV: V-Dem Liberal Democracy Index")

@@

result_ecm1 <- bind_rows(
    mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "Error-Correction Model",
           model = "Model 1.1 (ECM)")

result_fd1 <- bind_rows(
    mutate(result_clsAPSR[["fd1"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "First-Difference Model",
           model = "Model 1.3 (FD)")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
    filter(term != "(Intercept)") %>%
    mutate(
        term0 = c(rep(
            c("Democratic Mood\n (t-1)",
              "Democratic Mood\n (t-2)",
              "Liberal Democracy\n (Difference)",
              "Liberal Democracy\n (t-1)",
              "Log GDP\n per capita\n (Difference)",
              "Log GDP\n (t-1)"),
            time = 3),
            rep(
                c("Liberal Democracy\n (Difference)", 
                  "Log GDP\n per capita\n (Difference)"), 
                time = 3
            )),
        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
        model = factor(model, levels = paste0("Model ", 
                                              rep(1:2, each = 4), ".", rep(1:4, 2),
                                              " (",
                                              rep(c("ECM", "ECM", "FD", "FD"), 2),
                                              ")"))
    )

# result_apsrPooled <- result_APSR1 %>% 
#     filter(type == "Error-Correction Model") %>% 
#     mutate(type = "Pooled")

@@

result_ecmReg1 <- bind_rows(
    mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "Error-Correction Model",
           model = "Model 2.1 (ECM)")

result_fdReg1 <- bind_rows(
    mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "First-Difference Model",
           model = "Model 2.3 (FD)")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
    filter(term != "(Intercept)") %>%
    mutate(
        term0 = c(rep(
            c("Democratic Mood\n (t-1)",
              "Democratic Mood\n (t-2)",
              "Electoral Democracy\n (Difference)",
              "Electoral Democracy\n (t-1)",
              "Minoritarian Democracy\n (Difference)",
              "Minoritarian Democracy\n (t-1)",
              "Log GDP\n per capita\n (Difference)",
              "Log GDP\n (t-1)"),
            time = 3),
            rep(
                c("Electoral Democracy\n (Difference)", 
                  "Minoritarian Democracy\n (Difference)",
                  "Log GDP\n per capita\n (Difference)"), 
                time = 3
            )),
        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
        model = factor(model, levels = paste0("Model ", 
                                              rep(1:2, each = 4), ".", rep(1:4, 2),
                                              " (",
                                              rep(c("ECM", "ECM", "FD", "FD"), 2),
                                              ")"))
    )

# result_apsrRegime <- result_RegAPSR1 %>% 
#     filter(type == "Error-Correction Model") %>% 
#     mutate(type = "Institution Specified")

@@

result_ecm2 <- bind_rows(
    mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "Error-Correction Model",
           model = "Model 1.2 (ECM)")

result_fd2 <- bind_rows(
    mutate(result_clsAPSR[["fd2"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "First-Difference Model",
           model = "Model 1.4 (FD)")

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
    filter(term != "(Intercept)") %>%
    mutate(
        term0 = c(rep(
            c("Democratic Mood\n (t-1)",
              "Democratic Mood\n (t-2)",
              "Liberal Democracy\n (Difference)",
              "Liberal Democracy\n (t-1)",
              "Log GDP\n per capita\n (Difference)",
              "Log GDP\n (t-1)",
              "Corruption\n (Difference)",
              "Corruption\n (t-1)"
            ),
            time = 3),
            rep(
                c("Liberal Democracy\n (Difference)", 
                  "Log GDP\n per capita\n (Difference)",
                  "Corruption\n (Difference)"), 
                time = 3
            )),
        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
        model = factor(model, levels = paste0("Model ", 
                                                      rep(1:2, each = 4), ".", rep(1:4, 2),
                                                      " (",
                                                      rep(c("ECM", "ECM", "FD", "FD"), 2),
                                                      ")"))
    )

@@

result_ecmReg2 <- bind_rows(
    mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), submodel = "Uncertainty & More Data")) %>%
    mutate(type = "Error-Correction Model",
           model = "Model 2.2 (ECM)")

result_fdReg2 <- bind_rows(
    mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), submodel = "Uncertainty & More Data")) %>% 
    mutate(type = "First-Difference Model",
           model = "Model 2.4 (FD)")

result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
    filter(term != "(Intercept)") %>%
    mutate(
        term0 = c(rep(
            c("Democratic Mood\n (t-1)",
              "Democratic Mood\n (t-2)",
              "Electoral Democracy\n (Difference)",
              "Electoral Democracy\n (t-1)",
              "Minoritarian Democracy\n (Difference)",
              "Minoritarian Democracy\n (t-1)",
              "Log GDP\n per capita\n (Difference)",
              "Log GDP\n (t-1)",
              "Corruption\n (Difference)",
              "Corruption\n (t-1)"
            ),
            time = 3),
            rep(
                c("Electoral Democracy\n (Difference)", 
                  "Minoritarian Democracy\n (Difference)",
                  "Log GDP\n per capita\n (Difference)",
                  "Corruption\n (Difference)"), 
                time = 3
            )),
        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
        model = factor(model, levels = paste0("Model ", 
                                              rep(1:2, each = 4), ".", rep(1:4, 2),
                                              " (",
                                              rep(c("ECM", "ECM", "FD", "FD"), 2),
                                              ")"))
    )
```

```{r coefName-APSR}
index_coefName <- c(
    `Democratic Mood\n (t-1)` = "Democratic~Support[t-1]",
    `Democratic Mood\n (t-2)` = "Democratic~Support[t-2]",
    `Liberal Democracy\n (Difference)` = "Delta~Liberal~democracy",
    `Liberal Democracy\n (t-1)` = "Liberal~Democracy[t-1]",
    `Electoral Democracy\n (Difference)` = "Delta~Electoral~Democracy",
    `Electoral Democracy\n (t-1)` = "Electoral~Democracy[t-1]",
    `Minoritarian Democracy\n (Difference)` = "Delta~Minoritarian~Democracy",
    `Minoritarian Democracy\n (t-1)` = "Minoritarian~Democracy[t-1]",
    `Log GDP\n per capita\n (Difference)` = "Delta~Log~GDP~per~capita",
    `Log GDP\n (t-1)` = "Log~GDP[t-1]",
    `Corruption\n (Difference)` = "Delta~Corruption",
    `Corruption\n (t-1)` = "Corruption[t-1]"
)
```

```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on Change in Public Support with Uncertainty", fig.width=7, fig.height=10}
df_plot <- bind_rows(result_APSR1, result_APSR2,
                     result_RegAPSR1, result_RegAPSR2) %>% 
    mutate(term = index_coefName[term0], 
           term = factor(term, levels = unique(index_coefName)))

small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
    theme_bw() +
    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
    scale_color_grey(start = 0.8, end = 0.4, 
                     name = "Replication",
                     breaks=c("Point Estimates Only",
                              "With Uncertainty",
                              "Uncertainty & More Data"),
                     labels=c("Point Estimates Only",
                              "With Uncertainty",
                              "Uncertainty & More Data")) +
    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
          strip.text.y.left = element_text(angle = 0),
          legend.position = c(0, -.01),
          legend.justification = c(1, 1), 
          legend.title = element_text(size = 9, face = "bold"),
          legend.title.align = 0.5,
          legend.text = element_text(size = 8),
          legend.background = element_rect(color="gray90"),
          legend.spacing = unit(-3, "pt"),
          legend.key.size = unit(7, "mm")) +
    ggtitle("DV: Change in Public Support for Democracy")
